The MacLeish Package: R Package for analyzing weather and spatial data

### 2022-06-06 joss_paper/paper.Rmd
moved trail map image

```{r macleish, echo = FALSE, fig.cap="Map of MacLeish Field Station, Whately, Massachusetts, USA.", out.width="50%"}
knitr::include_graphics(path = "macleish.jpg")
```

>>>>

```{r download-trail-map, include=FALSE, eval=FALSE}
download.file(
  url = "http://masstrails.com/cache/1007_0.jpg", 
  destfile = here::here("joss_paper", "macleish_trail_map.jpg")
)
```

```{r macleish, echo = FALSE, fig.cap="Map of MacLeish Field Station, Whately, Massachusetts, USA.", out.width="50%"}
knitr::include_graphics(here::here("joss_paper", "macleish_trail_map.jpg"))
```
